The eclipse of ASASSN-21qj: A planetary collision afterglow\\ and transit of the resultant debris cloud

### 2023-03-17 src/tex/ms.tex
[showyourwork] overleaf sync

\subsection{Stars}
The bRing project can observe 157 bright stars with a magnitude brighter than 4.
%
154 of these stars are marked in red in the Hertzsprung-Russell (HR) diagram in \ref{HRD}. For the three missing stars, no parallax was found.
%
This HR diagram is made using data from an all-sky catalogue \citep{Kharchenko_2001}.
%
We use the parallaxes of the stars and their V and B magnitudes. The absolute magnitude is computed as follows:
\begin{align}
    M = m_V -5\log\left(\frac{1}{\pi}\right) + 5
\end{align}
$M$ is the absolute magnitude and $m_V$ is the apparent V-magnitude. $\pi$ is the parallax in arcseconds.
%
Most of the stars with a magnitude brighter than 4 are found in the upper part of the HR diagram, because they are all very bright.
%
A little over half of the bright stars lie on the main sequence and on the right of the main sequence a lot of giants can be found.
%
For reference, the Sun and Vega are also displayed in the figure.
%
Vega is one of the brightest stars in the northern hemisphere with a B-V colour of 0.
%
Using the B-V colour, the bright stars are found to have spectral type B to K.
%
A few stars have spectral type M. 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{HR_final.png}
    \caption{This plot presents 154 of the 157 stars for which we make light curves in red.
      %
      The grey dots represent all of the stars which are observed by bRing.
      %
      The Sun is plotted in yellow and Vega in light blue (both of which are not observed by bRing).
      %
      On the vertical axis the absolute magnitude is displayed and on the horizontal axis the B-V colour scale is shown.}
    \label{HRD}
  \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{bRing.jpg}
    \caption{The bRing instrument. Reprinted from \cite{bring}, figure 5.}
    \label{bRing}
\end{figure}

@@

%teveel 'show'
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{delta_Cent_first3.png}
    \caption{The first three steps of the data reduction are shown here. The first plot shows the raw data that was saved by bRing. The second plot shows the data without the long exposures. Lastly, the data without the bad photometry and astrometry flags is plotted. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
    \label{deltaCen1}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{delta_Cent_second3.png}
    \caption{This figure shows the next three steps of the data reduction. The first step is to make sure that the magnitude error is always finite and greater than zero. Next, the data where the altitude of the Sun is not below $-18^o$ is removed. In the last plot the 3$\sigma$ outliers on the mean of the cloud error are removed. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. Note that the magnitude scale is different for the last plot.}
    \label{deltaCen2}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{delta_Cent_last3.png}
    \caption{This figure shows the last three steps of the data reduction. First, the 5$\sigma$ outliers of the mean of the magnitude error are removed. In the second plot the 3$\sigma$ outliers on the mean of the cloud are removed. Lastly, the 5$\sigma$ outliers on the sky background are removed. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. Note that the magnitude scale differs for each plot.}
    \label{deltaCen3}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Mimosa_detrend_steps.png}
    \caption{This figure shows the steps for detrending a non-variable star. The first plot shows the data before detrending.
    The second plot shows the data after detrending the LSTSEQ. The third plot shows the data after detrending per Julian Date. The final plot shows the data after detrending for the moon. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
    \label{Mimosa_detrend_steps}
\end{figure}
%uitleg over figuren
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Mimosa_detrending.png}
    \caption{This figure shows the difference in the light curves before and after detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
    \label{Mimosa_detrend}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Mimosa_detrending_zoom.png}
    \caption{This figure shows the difference in the light curves before and after detrending on a daily scale. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The plot is zoomed in on the horizontal axis.}
    \label{Mimosa_detrend_zoom}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Mimosa_bin.png}
    \caption{This figure shows the detrended data of a star before and after binning. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
    \label{Mimosa_bin}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Canopus_thesis.png}
    \caption{Light curve of Canopus after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Canopus is 2111805.}
    \label{Canopus}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Rigil_Kentaurus_thesis.png}
    \caption{Light curve of Rigil Kentaurus after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Rigil Kentaurus is 2348878.}
    \label{Rigil_Kentaurus}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Achernar_thesis.png}
    \caption{Light curve of Achernar after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Achernar is 2199019.}
    \label{Achernar}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Hadar_thesis.png}
    \caption{Light curve of Hadar after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Hadar is 2345078.}
    \label{Hadar}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Acrux_thesis.png}
    \caption{Light curve of Acrux after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Acrux is 2333718.}
    \label{Acrux}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Mimosa_thesis.png}
    \caption{Light curve of Mimosa after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Mimosa is 2250231.}
    \label{Mimosa}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Shaula_thesis.png}
    \caption{Light curve of Shaula after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Shaula is 1880898.}
    \label{Shaula}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Gacrux_thesis.png}
    \caption{Light curve of Gacrux after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Gacrux is 2248482.}
    \label{Gacrux}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Miaplacidus_thesis.png}
    \caption{Light curve of Miaplacidus after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Miaplacidus is 2386073.}
    \label{Miaplacidus}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{Alnair_thesis.png}
    \caption{Light curve of Alnair after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Alnair is 2098110.}
    \label{Alnair}
\end{figure}
\end{enumerate}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{del_Pav_thesis.png}
    \caption{Light curve of delta Pavonis after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of delta Pavonis is 2424942.}
    \label{del_Pav}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{bet_Hyi_thesis.png}
    \caption{Light curve of beta Hydri after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of beta Hydri is 2430714.}
    \label{bet_Hyi}
  \end{figure}

@@

If a solution to this problem is discovered in the future, it should be possible to adapt the reduced data by adding in another data reduction step. The data reduction steps taken in this research could still be used in this case, and do not have to be repeated.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{thesis_histogram.png}
    \caption{Histograms showing the data before and after removing $5\sigma$ magnitude outliers. 200 bins were used for both histograms. The bRing catalogue magnitude value is 3.848 for this star, indicated by the dashed vertical line. The horizontal axis shows the magnitude. The ASCC-number for upsilon$^1$ Centauri is 1959875.}
    \label{hist}
\end{figure}
Another flaw in the data is that the values of the apparent magnitudes may not be accurate compared to other sources. An error remains in the calibration of the magnitudes, and therefore both absolute magnitude values as well as relative changes in magnitude are not completely accurate.
This is because the mean magnitude of the star is fixed to the visual magnitude in the bRing catalogue \citep{Talens_2018}, which is not always correct. The overall shape of fluctuations in magnitude is relatively good, but to determine the depth of transits and periods, follow-up observations are needed.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{burpdetrend.png}
    \caption{This figure shows two light curves of a star with ASCC-number 2295857. The first plot shows the light curve created using our calibration and the second plot shows the light curve using the calibration of BURP. The time in Julian Date is displayed on the horizontal axis and the apparent magnitude is displayed on the vertical axis.}

    \label{burp}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{burpdetrend_zoom.png}
    \caption{This figure shows the difference between our method of calibration and the method of burp. The light curve is shown on a daily scale and both plots have a corresponding vertical scale. The time in Julian Date is displayed on the horizontal axis and the apparent magnitude is displayed on the vertical axis.}
    \label{burpzoom}
\end{figure}

>>>>

\subsection{Stars}
The bRing project can observe 157 bright stars with a magnitude brighter than 4.
%
154 of these stars are marked in red in the Hertzsprung-Russell (HR) diagram in \ref{HRD}. For the three missing stars, no parallax was found.
%
This HR diagram is made using data from an all-sky catalogue \citep{Kharchenko_2001}.
%
We use the parallaxes of the stars and their V and B magnitudes. The absolute magnitude is computed as follows:
\begin{align}
    M = m_V -5\log\left(\frac{1}{\pi}\right) + 5
\end{align}
$M$ is the absolute magnitude and $m_V$ is the apparent V-magnitude. $\pi$ is the parallax in arcseconds.
%
Most of the stars with a magnitude brighter than 4 are found in the upper part of the HR diagram, because they are all very bright.
%
A little over half of the bright stars lie on the main sequence and on the right of the main sequence a lot of giants can be found.
%
For reference, the Sun and Vega are also displayed in the figure.
%
Vega is one of the brightest stars in the northern hemisphere with a B-V colour of 0.
%
Using the B-V colour, the bright stars are found to have spectral type B to K.
%
A few stars have spectral type M. 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/HR_final.png}
    \caption{This plot presents 154 of the 157 stars for which we make light curves in red.
      %
      The grey dots represent all of the stars which are observed by bRing.
      %
      The Sun is plotted in yellow and Vega in light blue (both of which are not observed by bRing).
      %
      On the vertical axis the absolute magnitude is displayed and on the horizontal axis the B-V colour scale is shown.}
    \label{HRD}
  \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.65\textwidth]{figures/bRing.jpg}
    \caption{The bRing instrument. Reprinted from \cite{bring}, figure 5.}
    \label{bRing}
\end{figure}

@@

%teveel 'show'
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/delta_Cent_first3.png}
    \caption{The first three steps of the data reduction are shown here. The first plot shows the raw data that was saved by bRing. The second plot shows the data without the long exposures. Lastly, the data without the bad photometry and astrometry flags is plotted. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
    \label{deltaCen1}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/delta_Cent_second3.png}
    \caption{This figure shows the next three steps of the data reduction. The first step is to make sure that the magnitude error is always finite and greater than zero. Next, the data where the altitude of the Sun is not below $-18^o$ is removed. In the last plot the 3$\sigma$ outliers on the mean of the cloud error are removed. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. Note that the magnitude scale is different for the last plot.}
    \label{deltaCen2}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/delta_Cent_last3.png}
    \caption{This figure shows the last three steps of the data reduction. First, the 5$\sigma$ outliers of the mean of the magnitude error are removed. In the second plot the 3$\sigma$ outliers on the mean of the cloud are removed. Lastly, the 5$\sigma$ outliers on the sky background are removed. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. Note that the magnitude scale differs for each plot.}
    \label{deltaCen3}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Mimosa_detrend_steps.png}
    \caption{This figure shows the steps for detrending a non-variable star. The first plot shows the data before detrending.
    The second plot shows the data after detrending the LSTSEQ. The third plot shows the data after detrending per Julian Date. The final plot shows the data after detrending for the moon. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
    \label{Mimosa_detrend_steps}
\end{figure}
%uitleg over figuren
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Mimosa_detrending.png}
    \caption{This figure shows the difference in the light curves before and after detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
    \label{Mimosa_detrend}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Mimosa_detrending_zoom.png}
    \caption{This figure shows the difference in the light curves before and after detrending on a daily scale. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The plot is zoomed in on the horizontal axis.}
    \label{Mimosa_detrend_zoom}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Mimosa_bin.png}
    \caption{This figure shows the detrended data of a star before and after binning. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis.}
    \label{Mimosa_bin}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Canopus_thesis.png}
    \caption{Light curve of Canopus after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Canopus is 2111805.}
    \label{Canopus}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Rigil_Kentaurus_thesis.png}
    \caption{Light curve of Rigil Kentaurus after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Rigil Kentaurus is 2348878.}
    \label{Rigil_Kentaurus}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Achernar_thesis.png}
    \caption{Light curve of Achernar after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Achernar is 2199019.}
    \label{Achernar}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Hadar_thesis.png}
    \caption{Light curve of Hadar after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Hadar is 2345078.}
    \label{Hadar}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Acrux_thesis.png}
    \caption{Light curve of Acrux after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Acrux is 2333718.}
    \label{Acrux}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Mimosa_thesis.png}
    \caption{Light curve of Mimosa after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Mimosa is 2250231.}
    \label{Mimosa}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Shaula_thesis.png}
    \caption{Light curve of Shaula after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Shaula is 1880898.}
    \label{Shaula}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Gacrux_thesis.png}
    \caption{Light curve of Gacrux after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Gacrux is 2248482.}
    \label{Gacrux}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Miaplacidus_thesis.png}
    \caption{Light curve of Miaplacidus after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Miaplacidus is 2386073.}
    \label{Miaplacidus}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/Alnair_thesis.png}
    \caption{Light curve of Alnair after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of Alnair is 2098110.}
    \label{Alnair}
\end{figure}
\end{enumerate}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/del_Pav_thesis.png}
    \caption{Light curve of delta Pavonis after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of delta Pavonis is 2424942.}
    \label{del_Pav}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/bet_Hyi_thesis.png}
    \caption{Light curve of beta Hydri after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of beta Hydri is 2430714.}
    \label{bet_Hyi}
  \end{figure}

@@

If a solution to this problem is discovered in the future, it should be possible to adapt the reduced data by adding in another data reduction step. The data reduction steps taken in this research could still be used in this case, and do not have to be repeated.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/thesis_histogram.png}
    \caption{Histograms showing the data before and after removing $5\sigma$ magnitude outliers. 200 bins were used for both histograms. The bRing catalogue magnitude value is 3.848 for this star, indicated by the dashed vertical line. The horizontal axis shows the magnitude. The ASCC-number for upsilon$^1$ Centauri is 1959875.}
    \label{hist}
\end{figure}
Another flaw in the data is that the values of the apparent magnitudes may not be accurate compared to other sources. An error remains in the calibration of the magnitudes, and therefore both absolute magnitude values as well as relative changes in magnitude are not completely accurate.
This is because the mean magnitude of the star is fixed to the visual magnitude in the bRing catalogue \citep{Talens_2018}, which is not always correct. The overall shape of fluctuations in magnitude is relatively good, but to determine the depth of transits and periods, follow-up observations are needed.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/burpdetrend.png}
    \caption{This figure shows two light curves of a star with ASCC-number 2295857. The first plot shows the light curve created using our calibration and the second plot shows the light curve using the calibration of BURP. The time in Julian Date is displayed on the horizontal axis and the apparent magnitude is displayed on the vertical axis.}

    \label{burp}
\end{figure}
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/burpdetrend_zoom.png}
    \caption{This figure shows the difference between our method of calibration and the method of burp. The light curve is shown on a daily scale and both plots have a corresponding vertical scale. The time in Julian Date is displayed on the horizontal axis and the apparent magnitude is displayed on the vertical axis.}
    \label{burpzoom}
\end{figure}
